
# Predicting Credit Card Fraud
## Sijith
### July 11, 2021



## Project Objective


* The objective of this project is to predict which credit card transactions in the dataset are fraudulent using three classification algorithms and three synthetic balancing techniques. The three classifier algorithms we will train include:

** Decision Tree, which uses a tree-like model of decisions to arrive at a classification prediction.
** Naive Bayes, which uses Bayes’ theorem to use probability to arrive at a classification prediction.
** Linear Discriminant Analysis, which finds a linear combination of features that is then used to separate the classes and arrive at a classification prediction.
* Given that the objective is to evaluate the model performance of the three classifier algorithms and synthetic balancing techniques, we will not be thoroughly reviewing the model output, but rather will be focusing on the classification performance results.

* Install and load the R library packages that will be used in this project, which are the caret, corrplot, and smotefamily packages.

```{r}
#Install packages
install.packages("caret")
install.packages("corrplot")
install.packages("smotefamily")
```

```{r}
#Load the packages
library(caret)
library(corrplot)
library(smotefamily)
```

# 1. Import and load the dataset

Next, using the “read.csv” function, we will import the credit card fraud dataset and set the class to a factor. This dataset is a subset of the dataset sourced from https://www.kaggle.com/mlg-ulb/creditcardfraud, which includes anonymized credit card transactions.

```{r}
#A. Load the dataset
creditcardFraud <- read.csv("Predicting_Credit_Card_Fraud/creditcardFraud.csv")

#B. Change class to factor the as.factor function encodes the vector as a factor or category
creditcardFraud$class<-as.factor(creditcardFraud$class)

head(creditcardFraud)
```

# 2. Explore The Data

* To train the the models, it is important that we first understand and explore our data as it helps us identify potential data quality issues and it provides us the needed context to develop an appropriate model.  

* Explore the data and perform a high-level exploratory data analysis (EDA) of the dataset

```{r}
#A. Structure of the dataset
str(creditcardFraud)
```

```{r}
install.packages("tidyverse") #Should have done this earlier. I wanted this to use the view() function. Not important for this project.
```
```{r}
library(tidyverse)
```

```{r}
view(creditcardFraud) #opens up a new window to show the table
```

```{r}
#B. Look for missing values
sum(is.na(creditcardFraud))
```
```{r}
#C. Check for imbalance in the dataset
summary(creditcardFraud$class)
```

```{r}
#another method
table(creditcardFraud$class)
```

```{r}
#For proportion percentages
prop.table(table(creditcardFraud$class))
```

We see that 99% of the transactions are not fraudulent and 1% is fraudulent


```{r}
prop.table(table(creditcardFraud$class))*100
```
To look at distribution of predictor variables by reviewing their histograms.

```{r}
#D. Compile histograms for each variable
par(mfrow = c(3,5)) #Change setting to view 3x5 charts
i <- 1
for (i in 1:30) 
{hist((creditcardFraud[,i]), main = paste("Distibution of ", colnames(creditcardFraud[i])), xlab = colnames(creditcardFraud[i]), col = "light blue")
}
```
Lets look at correlations among the numerical measures. Generate teh correlations and save them to an object. Use the for function to select only the numerical measures which are found in columns 1 to 30.


```{r}
#E. Compute the correlations among the variables
r <- cor(creditcardFraud[,1:30])
```

```{r}
corrplot(r, type="lower", tl.col = "black", tl.srt = 15)
```


#3. Split the Data into Training and Test Sets using Caret Package

It is important that when we evaluate the performance of a model, we do so on a dataset that the model has not previously seen. Therefore, we will split our dataset into a training dataset and a test dataset and to maintain the same level of imbalance as in the original dataset, we will use stratified sampling by “class.”

* Training Dataset: This is the random subset of your data used to initially fit (or train) your model.

* Test Dataset: This dataset used to provide an unbiased evaluation of the model fit on the training dataset.

```{r}
#A. Split data into training and testing dataset used for model building (training dataset) 

set.seed(1337) #(setting seed to 1337 to get similar results as training video) 

train <- createDataPartition(creditcardFraud$class,    #Generate a stratified sample using class variable
                             p=.70,                  #Our sample size will be 70% for Training &30% for Test
                             times=1,                #Sampling this only once
                             list=F)                 #set list = f otherwise it will come back as a list

```

Create data partitions using the train object that we created above



```{r}
#Identify/create training dataset
train.orig <- creditcardFraud[train,]  #Original Imbalanced Dataset - for our ref
```

```{r}
# Identify/create Test dataset
test <- creditcardFraud[-train,]
```

```{r}
#B. Check the proportion/dimensions of observations allocated to each group (We wanted a partion of 70 and 30. We are confirming of that is what we got)

dim(train.orig) / dim(creditcardFraud)
```
I had got “Numeric(0) as the output above. After a lot of scratching my head and going over”HELP" topics, I realised that I missed a “,” at the end of line 149 ¯_(ツ)_/¯

```{r}
dim(test) / dim(creditcardFraud)
```

```{r}
#C. Balance of classes for training dataset
prop.table(table(train.orig$class)) # Using proportion tables to evaluate the distribution of classes
```

99% non faudulent and 1% fraudulent

```{r}
#D. Class balance for test dataset
prop.table(table(test$class))
```

So both the datasets that we created has similar imbalanced distributions as our original dataset


#4. Compile Synthetically Balanced Training Datsets

Now that we have split our dataset into a training and test dataset, lets create three new synthetically balanced datasets from the one imbalanced training dataset. To do this we will be using the "smotefamily" R package and we will be trying out three different techniques: SMOTE, ADASYN, and DB-SMOTE. Below is a brief description of each:

* SMOTE (Synthetic Minority Oversampling Technique): A subset of data is taken from the minority class as an example. New synthetic similar examples are generated from the “feature space” rather than the “data space.”

* ADASYN (Adaptive Synthetic Sampling): A weighted distribution is used depending on each minority class according to their degree of learning difficulty. More synthetic observations are generated for some minority class instances that are more difficult to learn as compared to others 

* DB-SMOTE (Density Based SMOTE): This over-samples the minority class at the decision boundary and over-examines the region to maintain the majority class detection rate. These are more likely to be misclassified than those far from the border.

```{r}
#generate SMOTE Balanced training dataset

train.smote <- SMOTE(train.orig[,-31], train.orig[,31], K = 5)  # K = # of nearest neighbours

names(train.smote)
```

```{r}
train.smote <- train.smote$data
```

```{r}
train.smote$class <- as.factor(train.smote$class)
```

Do the same with ADASYN

```{r}
#ADASYN Balanced
train.adas <- ADAS(train.orig[,-31], train.orig[,31], K = 5)

train.adas <- train.adas$data

train.adas$class <- as.factor(train.adas$class)
```

And for the Density Based Smote



```{r}
#Density based SMOTE
train.dbsmote <- DBSMOTE(train.orig[,-31], train.orig[,31])
```
```{r}
train.dbsmote <- train.dbsmote$data
train.dbsmote$class <- as.factor(train.dbsmote$class)
```

#4.1 Evaluate Class distributions for Synthetic datasets

```{r}
#Class Distribution of SMOTE Balanced Dataset
prop.table(table(train.smote$class))
```
```{r}
#Class Distribution of ADASYN Balanced Dataset
prop.table(table(train.adas$class))
```
```{r}
#Class Distribution of DB SMOTE Balanced Dataset
prop.table(table(train.dbsmote$class))
```
###We see that we have a balanced dataset. There is 50% that are no and 50% that are yes

#5. Original Data: Train Decision Tree, Naive Bayes, and LDA Models

Now that we have our four training datasets;

  1. the original imbalanced training dataset,

  2. the SMOTE balanced training dataset,

  3. the ADASYN balanced training dataset, and

  4. the DB-SMOTE balanced training dataset,

We will use the ‘caret’ package to train three classifier models/classifications algorithms (decision tree, naive Bayes, linear discriminant analysis). Then we use the trained models to generate the predictions for the test dataset. The we will measure the accuracy of the predictions on our test dataset.

Before we train our models, there are certian settings that will be shared across all of our models and caret enables us to set those in a train control object.

Lets start by fitting the three classifier models using the original imbalanced training dataset. We will use repeated 10x cross validation for our models across all of our trained models. We have to set the training control parameters.

For that we create a object ctrl…

```{r}
#A. Global options that we will use across all of our trained models

ctrl <- trainControl(method = "cv",                        #use teh train control and do cross validation
                     number = 10,                          # Do cross validation 10 times
                     classProbs = TRUE,                    # And want to get our results as probabilities
                     summaryFunction = twoClassSummary)    #And store results as two class summary
```

BY using the original imbalanced dataset, use the train function to train a decision tree. We want to predict using all the variables

```{r}
#B. Decision Tree: original data

dt_orig <- train(class~.,                #Using original dataset, use train function to predict class. ~. indicates that we are going to be using all of the variables
                 data = train.orig,      #identify teh dataset, 
                 method = "rpart",       # rpart is a cart which is a decision tree model
                 trControl = ctrl,       # train control identifies the parameters and how it will be validated
                 metric = "ROC")         #metrics to select the best model
```

```{r}
#install.packages("naivebayes")
library(naivebayes)
```

```{r}
#C. Naive Bayes regression: original data

nb_orig <- train(class~.,               
                 data = train.orig,     
                 method = "naive_bayes", 
                 trControl = ctrl,    
                 metric = "ROC")
```

```{r}
#D. Linear Discriminant Analysis: original data

lda_orig <- train(class~.,               
                 data = train.orig,     
                 method = "lda",      
                 trControl = ctrl,    
                 metric = "ROC")
```


#5.1 Compile Classifications on Test Data using models trained on the original imbalanced training dataset

Next, we will use the models we have trained using the original imbalanced training dataset to generate predictions on the test dataset.

* We will then compile three measures of performance, which we will use to compare the performance of the models across all of our trained models:

** Precision = TP / (TP+FP) - measures proportion of positive cases that are truly positive
** Recall = TP / (TP+FN) - measures how complete the results are. This is often also called the senSitivity
** F1 measure = (2xPrecision*Recall)/(Recall+Precision) - this combines the precision and recall into a single number

```{r}
###################################################
#Decision Tree Model - Trained on original dataset#
###################################################

#A. Decision Tree Model predictions

dt_orig_pred <- predict(dt_orig, test, type = "prob") # This will generate the predictions
```

```{r}
#B. Decision Tree - Assign class to probabilities
#generate Yes No classifications using the ifelse statement

dt_orig_test <- factor(ifelse(dt_orig_pred$yes>0.50, "yes", "no"))
```

To compare the model performance use the precision recall and the F one measure. Precision measures the proportion of positive cases that are truly positive. Recall which is also known as sensitivity is the fraction of the total amount of positive or fraudulent cases that were actually identified. F one measure is the harmonic mean of the precision and recall. For the purposes of our fraudulent transaction problem, the recall measure or our ability to identify the actual fraudulent cases is the most important for our classification problem.

```{r}
#C. Decision Tree Save Precision/Recall/F

precision_dtorig <- posPredValue (dt_orig_test, test$class, positive = "yes")

recall_dtorig <- sensitivity (dt_orig_test, test$class, positive = "yes")

F1_dtorig <- (2*precision_dtorig * recall_dtorig)/(precision_dtorig + recall_dtorig)
```

We just generated predictions as well as performance measures on our test dataset for the Decision Tree model.

```{r}
#################################################
#Naive Bayes Model - Trained on original dataset#
#################################################
#A. NB Model predictions
nb_orig_pred <- predict(nb_orig, test, type = "prob")

#B. NB - Assign class to probabilities
nb_orig_test <- factor(ifelse(nb_orig_pred$yes>0.50, "yes", "no"))


#C. NB Save Precision/Recall/F
precision_nborig <- posPredValue (nb_orig_test, test$class, positive = "yes")
recall_nborig <- sensitivity (nb_orig_test, test$class, positive = "yes")
F1_nborig <- (2*precision_nborig * recall_nborig)/(precision_nborig + recall_nborig)
```

```{r}
#########################################
#LDA Model - Trained on original dataset#
#########################################
#A. LDA Model predictions
lda_orig_pred <- predict(lda_orig, test, type = "prob")


#B. LDA - Assign class to probabilities
lda_orig_test <- factor(ifelse(lda_orig_pred$yes>0.50, "yes", "no"))


#C. LDA Save Precision/Recall/F
precision_ldaorig <- posPredValue (lda_orig_test, test$class, positive = "yes")
recall_ldaorig <- sensitivity (lda_orig_test, test$class, positive = "yes")
F1_ldaorig <- (2*precision_ldaorig * recall_ldaorig)/(precision_ldaorig + recall_ldaorig)
```

#6. SMOTE Balanced Data: Train Decision Tree, Naive Bayes, and LDA Models

Next, We will train the three classifier models using the SMOTE balanced training dataset. To train the models, we can simply copy and paste the code we used to train the models in task 5, create new names for the models and change the data we are using to train our models using from ‘train.orig’ to the ‘train.smote’ dataset.

Use caret package to fit the three classification algorithms. Use the smote balanced training dataset to train the classifiers. Also generate the predictions for the test dataset and measure the accuracy of the predictions.

```{r}
#A. Decision Tree: SMOTE data
dt_smote <- train(class~.,                
                 data = train.smote,      
                 method = "rpart",       
                 trControl = ctrl,      
                 metric = "ROC")  


#B. Naive Bayes regression: SMOTE data
nb_smote <- train(class~.,               
                 data = train.smote,     
                 method = "naive_bayes",      
                 trControl = ctrl,    
                 metric = "ROC")


#C. Linear Discriminant Analysis: SMOTE data
lda_smote <- train(class~.,               
                 data = train.smote,     
                 method = "lda",      
                 trControl = ctrl,    
                 metric = "ROC")
```

#6.1: Compile predictions using models trained on the SMOTE balanced training dataset

Next, we will use the models we have trained using the SMOTE balanced training dataset to generate predictions on the test dataset, and we will compute our three performance measures. To complete this, we can copy the code from the earlier task and change the names of the output and models to reference the models trained using the SMOTE balanced training dataset.

```{r}
################################################
#Decision Tree Model - Trained on SMOTE dataset#
################################################
#A. Decision Tree Model predictions
dt_smote_pred <- predict(dt_smote, test, type = "prob")

#B. Decision Tree - Assign class to probabilities
dt_smote_test <- factor(ifelse(dt_smote_pred$yes>0.50, "yes", "no"))


#C. Decision Tree Save Precision/Recall/F
precision_dtsmote <- posPredValue (dt_smote_test, test$class, positive = "yes")
recall_dtsmote <- sensitivity (dt_smote_test, test$class, positive = "yes")
F1_dtsmote <- (2*precision_dtsmote * recall_dtsmote)/(precision_dtsmote + recall_dtsmote)
```


```{r}
##############################################
#Naive Bayes Model - Trained on SMOTE dataset#
##############################################
#A. NB Model predictions
nb_smote_pred <- predict(nb_smote, test, type = "prob")

#B. NB - Assign class to probabilities
nb_smote_test <- factor(ifelse(nb_smote_pred$yes>0.50, "yes", "no"))


#C. NB Save Precision/Recall/F
precision_nbsmote <- posPredValue (nb_smote_test, test$class, positive = "yes")
recall_nbsmote <- sensitivity (nb_smote_test, test$class, positive = "yes")
F1_nbsmote <- (2*precision_nbsmote * recall_nbsmote)/(precision_nbsmote + recall_nbsmote)
```

```{r}
######################################
#LDA Model - Trained on SMOTE dataset#
######################################
#A. LDA Model predictions
lda_smote_pred <- predict(lda_orig, test, type = "prob")


#B. LDA - Assign class to probabilities
lda_smote_test <- factor(ifelse(lda_smote_pred$yes>0.50, "yes", "no"))


#C. LDA Save Precision/Recall/F
precision_ldasmote <- posPredValue (lda_smote_test, test$class, positive = "yes")
recall_ldasmote <- sensitivity (lda_smote_test, test$class, positive = "yes")
F1_ldasmote <- (2*precision_ldasmote * recall_ldasmote)/(precision_ldasmote + recall_ldasmote)
```

#7. Train Decision Tree, Naive Bayes, and LDA Models using ADASYN Balanced Data, generate predictions and measure the accuracy of the predictions.

In task 7, we will train the three classifier models using the ADASYN balanced training dataset. Again, to train the models, we can simply copy and paste the code we used to train the models in task 6, create new names for the model and change the data we are using to train our model to ‘train.adas’

```{r}
#A. Decision Tree: ADASYN data
dt_adas <- train(class~.,                
                 data = train.adas,      
                 method = "rpart",       
                 trControl = ctrl,      
                 metric = "ROC")  

#B. Naive Bayes regression: ADASYN data
nb_adas <- train(class~.,               
                 data = train.adas,     
                 method = "naive_bayes",      
                 trControl = ctrl,    
                 metric = "ROC")

#C. Linear Discriminant Analysis: ADASYN data
lda_adas <- train(class~.,               
                 data = train.adas,     
                 method = "lda",      
                 trControl = ctrl,    
                 metric = "ROC")
```


#7.1: Compile predictions using models trained on the ADASYN balanced training dataset

Next, we will use the models we have trained using the ADASYN balanced training dataset to generate predictions on the test dataset, and we will compute our three performance measures. To complete this, we can copy the code from the earlier task and change the names of the output and models to reference the models trained using the SMOTE balanced training dataset.

```{r}
#################################################
#Decision Tree Model - Trained on ADASYN dataset#
#################################################
#A. Decision Tree Model predictions
dt_adas_pred <- predict(dt_adas, test, type = "prob")

#B. Decision Tree - Assign class to probabilities
dt_adas_test <- factor(ifelse(dt_adas_pred$yes>0.50, "yes", "no"))


#C. Decision Tree Save Precision/Recall/F
precision_dtadas <- posPredValue (dt_adas_test, test$class, positive = "yes")
recall_dtadas <- sensitivity (dt_adas_test, test$class, positive = "yes")
F1_dtadas <- (2*precision_dtadas * recall_dtadas)/(precision_dtadas + recall_dtadas)
```

```{r}
###############################################
#Naive Bayes Model - Trained on ADASYN dataset#
###############################################
#A. NB Model predictions
nb_adas_pred <- predict(nb_adas, test, type = "prob")

#B. NB - Assign class to probabilities
nb_adas_test <- factor(ifelse(nb_adas_pred$yes>0.50, "yes", "no"))


#C. NB Save Precision/Recall/F
precision_nbadas <- posPredValue (nb_adas_test, test$class, positive = "yes")
recall_nbadas <- sensitivity (nb_adas_test, test$class, positive = "yes")
F1_nbadas <- (2*precision_nbadas * recall_nbadas)/(precision_nbadas + recall_nbadas)
```

```{r}
#######################################
#LDA Model - Trained on ADASYN dataset#
#######################################
#A. LDA Model predictions
lda_adas_pred <- predict(lda_orig, test, type = "prob")


#B. LDA - Assign class to probabilities
lda_adas_test <- factor(ifelse(lda_adas_pred$yes>0.50, "yes", "no"))


#C. LDA Save Precision/Recall/F
precision_ldaadas <- posPredValue (lda_adas_test, test$class, positive = "yes")
recall_ldaadas <- sensitivity (lda_adas_test, test$class, positive = "yes")
F1_ldaadas <- (2*precision_ldaadas * recall_ldaadas)/(precision_ldaadas + recall_ldaadas)
```

#8: DB-SMOTE Balanced Data: Train Decision Tree, Naive Bayes, and LDA Models

In task 8, we will train the three classifier models using the DB-SMOTE balanced training dataset. To train the models, we can simply copy and paste the code we used to train the models in task 7, create new names for the model and change the data we are using to train our model to ‘train.dbsmote’

```{r}
#A. Decision Tree: dbsmote data
dt_dbsmote <- train(class~.,                
                 data = train.dbsmote,      
                 method = "rpart",       
                 trControl = ctrl,      
                 metric = "ROC") 


#B. Naive Bayes regression: dbsmote data
nb_dbsmote <- train(class~.,               
                 data = train.dbsmote,     
                 method = "naive_bayes",      
                 trControl = ctrl,    
                 metric = "ROC")


#C. Linear Discriminant Analysis: dbsmote data
lda_dbsmote <- train(class~.,               
                 data = train.smote,     
                 method = "lda",      
                 trControl = ctrl,    
                 metric = "ROC")
```


#8.1: Compile predictions using models trained on the DB SMOTE balanced training dataset

Next, we will use the models we have trained using the DB-SMOTE balanced training dataset to generate predictions on the test dataset, and we will compute our three performance measures. To complete this, we can copy the code from the earlier task and change the names of the output and models to reference the models trained using the DB-SMOTE balanced training dataset.

```{r}
###################################################
#Decision Tree Model - Trained on DB SMOTE dataset#
###################################################
#A. Decision Tree Model predictions
dt_dbsmote_pred <- predict(dt_dbsmote, test, type = "prob")

#B. Decision Tree - Assign class to probabilities
dt_dbsmote_test <- factor(ifelse(dt_dbsmote_pred$yes>0.50, "yes", "no"))


#C. Decision Tree Save Precision/Recall/F
precision_dtdbsmote <- posPredValue (dt_dbsmote_test, test$class, positive = "yes")
recall_dtdbsmote <- sensitivity (dt_dbsmote_test, test$class, positive = "yes")
F1_dtdbsmote <- (2*precision_dtdbsmote * recall_dtdbsmote)/(precision_dtdbsmote + recall_dtdbsmote)
```

```{r}
#################################################
#Naive Bayes Model - Trained on DB SMOTE dataset#
#################################################
#A. NB Model predictions
nb_dbsmote_pred <- predict(nb_dbsmote, test, type = "prob")

#B. NB - Assign class to probabilities
nb_dbsmote_test <- factor(ifelse(nb_dbsmote_pred$yes>0.50, "yes", "no"))


#C. NB Save Precision/Recall/F
precision_nbdbsmote <- posPredValue (nb_dbsmote_test, test$class, positive = "yes")
recall_nbdbsmote <- sensitivity (nb_dbsmote_test, test$class, positive = "yes")
F1_nbdbsmote <- (2*precision_nbdbsmote * recall_nbdbsmote)/(precision_nbdbsmote + recall_nbdbsmote)
```

```{r}
#########################################
#LDA Model - Trained on DB SMOTE dataset#
#########################################
#A. LDA Model predictions
lda_dbsmote_pred <- predict(lda_orig, test, type = "prob")


#B. LDA - Assign class to probabilities
lda_dbsmote_test <- factor(ifelse(lda_dbsmote_pred$yes>0.50, "yes", "no"))


#C. LDA Save Precision/Recall/F
precision_ldadbsmote <- posPredValue (lda_dbsmote_test, test$class, positive = "yes")
recall_ldadbsmote <- sensitivity (lda_dbsmote_test, test$class, positive = "yes")
F1_ldadbsmote <- (2*precision_ldadbsmote * recall_ldadbsmote)/(precision_ldadbsmote + recall_ldadbsmote)
```

#9: Compare the model performance
We will compare the recall, precision, and F1 performance measures for each of the three models we trained using the four training datasets:

  1. original imbalanced,
  2. SMOTE balanced,
  3. ADASYN balanced, and
  4. DB SMOTE balanced.
  
Recall that the most important performance measure for the fraud problem is the recall, which measures how complete our results are indicating the model captures more of the fraudulent transactions. Recall is the fraction of the total positive or fraudulent cases that were actually identified by the model.

```{r}
#Lets reset the chart settings so we see one chart at a time
par(mfrow = c(1,1))
```

```{r}
#Compare the Recall of the models: TP / TP + FN. To do that, we'll need to combine our results into a dataframe[note update the names of the recall object if you used different names]

#To facilitate the comparison, create a dataframe that has two variables. The model name that denotes that dataset used to train the model and the recall object that we saved in tasks.

model_compare_recall <- data.frame(Model = c('DT-Orig',
                                      'NB-Orig',
                                      'LDA-Orig',
                                      'DT-SMOTE',
                                      'NB-SMOTE',
                                      'LDA-SMOTE',
                                      'DT-ADASYN',
                                      'NB-ADASYN',
                                      'LDA-ADASYN',
                                      'DT-DBSMOTE',
                                      'NB-DBSMOTE',
                                      'LDA-DBSMOTE' ),
                            Recall = c(recall_dtorig,
                                   recall_nborig,
                                   recall_ldaorig,
                                   recall_dtsmote,
                                   recall_nbsmote,
                                   recall_ldasmote,
                                   recall_dtadas,
                                   recall_nbadas,
                                   recall_ldaadas,
                                   recall_dtdbsmote,
                                   recall_nbdbsmote,
                                   recall_ldadbsmote))
```

```{r}
ggplot(aes(x=reorder(Model,-Recall) , y=Recall), data=model_compare_recall) +
  geom_bar(stat='identity', fill = 'light blue') +
  ggtitle('Comparative Recall of Models on Test Data') +
  xlab('Models')  +
  ylab('Recall Measure')+
  geom_text(aes(label=round(Recall,2)))+
  theme(axis.text.x = element_text(angle = 40))

```
We can see that the top three performing models are the decision trees trained on the synthetically balanced data. Specifically, the Decision Tree model trained using the ADASYN balanced dataset performed best followed by DBSMOTE and then SMOTE.

Now, lets compile the precision measures which is the fraction of the positive or fraudulent transactions among the positive cases that were identified.

```{r}
#Compare the Precision of the models: TP/TP+FP [note update the names of the precision object if you used different names]
model_compare_precision <- data.frame(Model = c('DT-Orig',
                                      'NB-Orig',
                                      'LDA-Orig',
                                      'DT-SMOTE',
                                      'NB-SMOTE',
                                      'LDA-SMOTE',
                                      'DT-ADASYN',
                                      'NB-ADASYN',
                                      'LDA-ADASYN',
                                      'DT-DBSMOTE',
                                      'NB-DBSMOTE',
                                      'LDA-DBSMOTE' ),
                              Precision = c(precision_dtorig,
                                         precision_nborig,
                                         precision_ldaorig,
                                         precision_dtsmote,
                                         precision_nbsmote,
                                         precision_ldasmote,
                                         precision_dtadas,
                                         precision_nbadas,
                                         precision_ldaadas,
                                         precision_dtdbsmote,
                                         precision_nbdbsmote,
                                         precision_ldadbsmote))
```

```{r}
ggplot(aes(x=reorder(Model,-Precision) , y=Precision), data=model_compare_precision) +
  geom_bar(stat='identity', fill = 'light green') +
  ggtitle('Comparative Precision of Models on Test Data') +
  xlab('Models')  +
  ylab('Precision Measure')+
  geom_text(aes(label=round(Precision,2)))+
  theme(axis.text.x = element_text(angle = 40))
```

Here, the LDA and Decision Tree models using the original data set performed better. But the naive Bayes model trained using the DB smote balanced dataset performed better than te naive Bayes model trained on the original imbalance dataset.

However, in aggregate the cost of not identifying fraudulent transactions can be very costly.

Therefore, the recall measure is the most important performance measure, and the results indicate that models trained using synthetically balanced training data have a superior recall performance relative to models trained using the original imbalance dataset

Lets compare the F one measures across the three different models.

```{r}
#Compare the F1 of the models: 2*((Precision*Recall) / (Precision + Recall)) [note update the names of the F1 object if you used different names]
model_compare_f1 <- data.frame(Model = c('DT-Orig',
                                      'NB-Orig',
                                      'LDA-Orig',
                                      'DT-SMOTE',
                                      'NB-SMOTE',
                                      'LDA-SMOTE',
                                      'DT-ADASYN',
                                      'NB-ADASYN',
                                      'LDA-ADASYN',
                                      'DT-DBSMOTE',
                                      'NB-DBSMOTE',
                                      'LDA-DBSMOTE' ),
                              F1 = c(F1_dtorig,
                                         F1_nborig,
                                         F1_ldaorig,
                                         F1_dtsmote,
                                         F1_nbsmote,
                                         F1_ldasmote,
                                         F1_dtadas,
                                         F1_nbadas,
                                         F1_ldaadas,
                                         F1_dtdbsmote,
                                         F1_nbdbsmote,
                                         F1_ldadbsmote))
```


```{r}
ggplot(aes(x=reorder(Model,-F1) , y=F1), data=model_compare_f1) +
  geom_bar(stat='identity', fill = 'light grey') +
  ggtitle('Comparative F1 of Models on Test Data') +
  xlab('Models')  +
  ylab('F1 Measure')+
  geom_text(aes(label=round(F1,2)))+
  theme(axis.text.x = element_text(angle = 40))
```

Here we see that the Decision Tree and the LDA Models for the original imbalanced dataset has a higher F one, and only the naive Bayes trained on the DB smote performed better. However, this is being driven by the higher performance in precision which is driving the F one measure higher.


